---
title: "Final Assignment for Developing Data Products"
author: "Kara Schimmelfing"
date: "1/20/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Aim

The goal of this project was to create a simple Shiny application and deploy it. Additionally to build a supporting presentation that you are currently viewing.

## Premise

I chose to use the Galton Families dataset that we used in a previous course to do a simple linear model prediction of a child's height based on their parent's height and gender. The idea was it was interactive so you could figure out any possible permutations of parents' heights you wanted. 

## Location

The Application can be found here: https://schimmelfing.shinyapps.io/heightscomparison/
GitHub Repository here: https://github.com/schimmelfing/FinalProjectShinyPitch

## Plot

```{r plot, warning =FALSE}
library(HistData)
##The data used in the app comes from the GaltonFamilies dataset. 
data(GaltonFamilies)
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight,xlab="Average Height of the Parents (in inches)",ylab="Height of the Child (in inches)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "green", "blue"))
legend(65,80,pch=c(19,19),col=c("green","blue"),c("female", "male"),bty="o",cex=.6)
```


